
---
title: "Homework 5"
author: DS Student
date: January 15, 2020
output: 
    pdf_document
---
## Randomly split the mcycle data into training (75%) and validation (25%) subsets.
```{r}
set.seed(10)
library('MASS')
data <- mcycle
train_data_ind <- sample(dim(data)[1], dim(data)[1]*0.75) 
train_data <- data[train_data_ind,]
test_data <- data[-train_data_ind,]
train_y <- train_data$accel
train_x <- matrix(train_data$times, length(train_data$times), 1)
test_y <- test_data$accel
test_x <- matrix(test_data$times, length(test_data$times), 1)

```


## Using the mcycle data, consider predicting the mean acceleration as a function of time. Use the Nadaraya-Watson method with the k-NN kernel function to create a series of prediction models by varying the tuning parameter over a sequence of values. (hint: the script already implements this)

```{r}

Nadaraya_Watson <- function(y,x,x0,kern,...){
  a <- t(apply(x0, 1, function(x0_){
    k <- kern(x,x0_,...)
    k/sum(k)
    }))

    y_hat <- drop(a %*% y)
    attr(y_hat,"k") <- a
    return(y_hat)
}

kernel_k_nearest_neighbors <- function(x, x0, t=1) {
  ## compute distance betwen each x and x0
  z <- t(t(x) - x0)
  d <- sqrt(rowSums(z*z))

  ## initialize kernel weights to zero
  w <- rep(0, length(d))
  
  ## set weight to 1 for k nearest neighbors
  w[order(d)[1:t]] <- 1
  
  return(w)
}
k1 <- seq(1,20,1)
for (i in k1){
  y_hat <- Nadaraya_Watson(y = train_y,x = train_x,x0 = test_x, kern = kernel_k_nearest_neighbors, t = i)
}

```

## With the squared-error loss function, compute and plot the training error, AIC, BIC, and validation error (using the validation data) as functions of the tuning parameter.
```{r}
effective_df <- function(y, x, kern, ...) {
  y_hat <- Nadaraya_Watson(y, x, x,
    kern=kern, ...)
  sum(diag(attr(y_hat, 'k')))
}


loss_squared_error <- function(y, yhat)
  (y - yhat)^2

error <- function(y, yhat, loss=loss_squared_error)
  mean(loss(y, yhat))

aic <- function(y, yhat, d)
  error(y, yhat) + 2/length(y)*d

bic <- function(y, yhat, d)
  error(y, yhat) + log(length(y))/length(y)*d

AIC <- rep(0,1)
BIC <- rep(0,1)
training_error <- rep(0,1)
testing_error <- rep(0,1)
s = 1

for (i in (1:length(k1))){
  edf <- effective_df(train_y, train_x, kernel_k_nearest_neighbors, t=k1[i])
  y_hat_train <- Nadaraya_Watson(y = train_y,x = train_x,x0 = train_x, kern = kernel_k_nearest_neighbors, t = k1[i])
  y_hat_test <- Nadaraya_Watson(y = train_y,x = train_x,x0 = test_x, kern = kernel_k_nearest_neighbors, t = k1[i])
  AIC[i] <- aic(train_y, y_hat_train,edf)
  BIC[i] <- bic(train_y, y_hat_train,edf)
  training_error[i] <- error(train_y, y_hat_train)
  testing_error[i] <- error(test_y, y_hat_test)
}
print(training_error)
print(testing_error)
print(AIC)
print(BIC)

plot(k1,training_error,type = "l", col = "green",ylim = c(180,1300),xlab = "k",ylab = "error")
lines(k1,AIC,col = "pink",type = "l")
lines(k1,BIC,col = "lightblue",type = "l")
lines(k1,testing_error,col = "red",type = "l")
legend("topright", c("training error", "AIC", "BIC", "Validation error"), col = c("green","pink","lightblue","red"),lty = 1)

```


## For each value of the tuning parameter, Perform 5-fold cross-validation using the combined training and validation data. This results in 5 estimates of test error per tuning parameter value.
```{r,warning = FALSE}
f <- 5
k1 <- seq(1,20,1)
folds <- sample(rep(1:5,length(data)))
err <- rep(0,1)
for (i in (1:length(k1))){
  e <- rep(0,5)
  for (j in (1:5)){
    train_y <- train_data$accel[folds!= j]
    train_x <- matrix(data$times[folds!= j], length(train_data$times[folds!= j]), 1)
    test_y <- test_data$accel
    test_x <- matrix(test_data$times[folds== j], length(test_data$times[folds== j]), 1)
    # train model
    y_hat <- Nadaraya_Watson(y = train_y,x = train_x,x0 = test_x, kern = kernel_k_nearest_neighbors, t = k1[i])
    # error of every validation
    
    e[j] <- error(test_y, y_hat)
  }
  print(e)
  err[i] <- mean(e)
}

```



## Plot the CV-estimated test error (average of the five estimates from each fold) as a function of the tuning parameter. Add vertical line segments to the figure (using the segments function in R) that represent one “standard error” of the CV-estimated test error (standard deviation of the five estimates from each fold).
```{r}
sd <- sd(err)
plot(k1,err,type = "l",col = "red", ylim = c(500,6000))
abline(h = sd)
legend("topright",c("error", "sd"), col = c("red", "black"),lty = 1 )
```


## Interpret the resulting figures and select a suitable value for the tuning parameter.
From the plot we can see that when k = 8, the test and train plot is the smallest. When k >8 and k increases, test and train error also increase. Waht's more, AIC, BIC are similar with the train error. Therefore, suitable k value is about 8.

